Exploring probability distributions for bivariate temporal granularities

### 2019-09-16 main.Rmd
playing with cricekt example

z is the index set of the tsibble, x,y are two linear granularities with  $order(x) <  order(y)$. Also, $f(x, y)$ denotes the accessor function for computing circular granularity x_y and $c(x, y)$ is a constant which relates x and y. It is easy to see that for $order(x+1) =  order(y)$, the function is same as the single-order-up granularities.

@@

```{r table_accessor2}
kable(tibble::tibble(
  `linear granularities` = c("minute", "hour", "day", "month", "quarter", "year"),
  `Conversion factor` = c(60,24, "aperiodic", 3, 4, 1), format = "markdown")
```

@@

```{r read_data, echo=FALSE}

@@

@@

>>>>

z is the index set of the tsibble and x, y are two linear granularities with  $order(x) <  order(y)$. Also, $f(x, y)$ denotes the accessor function for computing circular granularity x_y and $c(x, y)$ is a constant which relates x and y. It is easy to see that for $order(x+1) =  order(y)$, the function is same as the single-order-up granularities.

@@

```{r table_accessor2}
kable(tibble::tibble(
  `linear granularities` = c("minute", "hour", "day", "month", "quarter", "year"),
  `Conversion factor` = c(60,24, "aperiodic", 3, 4, 1), format = "markdown"))
```

@@

Only for 2008
```{r read_data, echo=FALSE}

@@

```{r read_data_all_seas, echo=FALSE}

load("/Users/sgup0008/Documents/paper-gravitas/data/cricket_all_seas.rda")

cricket_tsibble_all <- cricket_all_seas %>%
  filter(season %in% c(2012:2015)) %>% 
  mutate(data_index = row_number()) %>%
  as_tsibble(index = data_index)

#over_inning    ball_over 
cricket_tsibble_all %>% granplot("over_inning", "ball_over",
  hierarchy_model,
  response = "total_runs",
  plot_type = "quantile",
  quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)

cricket_tsibble_all %>% granplot("inning_match", "ball_over",
  hierarchy_model,
  response = "total_runs",
   plot_type = "quantile",
  quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)
)

# inning_match   ball_inning 
#interesting plot
cricket_tsibble_all %>% granplot("inning_match", "ball_inning",
  hierarchy_model,
  response = "total_runs",
   plot_type = "quantile",
  quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9))+
  scale_x_discrete(breaks = seq(1,120,5))

cricket_tsibble_all %>% granplot("ball_over", "over_inning",
  hierarchy_model,
  response = "total_runs",
  plot_type = "quantile",
  quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9))

cricket_tsibble_all %>% granplot("inning_match", "over_inning",
  hierarchy_model,
  response = "total_runs"
)

cricket_tsibble_all %>% granplot("ball_over", "over_match",
  hierarchy_model,
  response = "total_runs"
)

cricket_tsibble_all %>% granplot("ball_over", "inning_match",
  hierarchy_model,
  response = "total_runs"
) + scale_color_brewer(type = "div", palette = "Dark2")

cricket_tsibble_all %>%
  granplot(
    gran1 = "inning_match",
    gran2 = "over_inning",
    hierarchy_model,
    response = "total_runs",
    plot_type = "quantile"
  )
```

@@

```{r runs_per-over}

# all season per over runs
cricket_per_over_all <- cricket_all_seas %>% 
  group_by(season, match_id, batting_team,inning, over) %>%
  summarise(runs_per_over = sum(total_runs))

# all season per over runs tsibble
cricket_tsibble_all <- cricket_per_over_all %>% 
  ungroup() %>% 
  mutate(data_index = row_number()) %>% 
  as_tsibble(index = data_index)

  cricket_tsibble_all %>% granplot("inning_match", "over_inning",
                               hierarchy_model,
                               response = "runs_per_over",
                               plot_type = "quantile",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)

  cricket_tsibble_all %>% granplot("inning_match", "season",
                               hierarchy_model,
                               response = "runs_per_over",
                               plot_type = "quantile",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)

  cricket_tsibble_all %>% granplot("season", "over_inning",
                               hierarchy_model,
                               response = "runs_per_over",
                               plot_type = "quantile",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)
